### 2025-08-13 getting-started.qmd
20250813 - clarification

::: {#nte-gettingStarted .callout-note title="If you are in Professor Petersen's class"}
If you are in Professor Petersen's class, also perform the following steps:

>>>>

::: {#nte-gettingStarted .callout-note title="If you are in Professor Petersen's class"}
If you are in Professor Petersen's class, also perform the following steps, to set up version control and your blog:
